Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real

### 2022-06-23 CORL/appendix.tex
Appendix: Added subsection{Training Procedures}

	The exact equation for $\lUC$ is as follows:
	to formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
	with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
	%Jinghyan's Version (uses expectation)
	% \begin{equation}
	% 	\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
	% 	\eqand \bar{\unprojection}^i_{u,v}   =   
	% 		\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
	% 	\eqand 
	% 	%\lUC=\frac{\lsum_{i,U,V}
	% 	%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
	% 	%{128\cdot128\cdot L}
	% 	\lUC=\mathbb{E}\left[
	% 	\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
	% \end{equation}
	%
	%
	%Unabbreviated: Not Jinguan's version; 
	\begin{equation}
		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
		\eqand \bar{\unprojection}^i_{c,u,v}   =   
			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
		\eqand 
		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
		\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
		{3\cdot128\cdot128\cdot L}
	\end{equation}
	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
	%  $(u,v,l)=s^n_{1...3,x,y}$
	$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
	for all 
	$n \in \{1...N\}$ , 
	$i \in \{1...L\}$ , 
	$x \in \{1...W\}$ , 
	$y \in \{1...H\}$ , 
	$U \in \{1...128\}$ , 
	$V \in \{1...128\}$.

@@

\subsection{More Results}

>>>>

	The exact equation for $\lUC$ is as follows:
	to formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
	with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
	%Jinghyan's Version (uses expectation)
	% \begin{equation}
	% 	\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
	% 	\eqand \bar{\unprojection}^i_{u,v}   =   
	% 		\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
	% 	\eqand 
	% 	%\lUC=\frac{\lsum_{i,U,V}
	% 	%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
	% 	%{128\cdot128\cdot L}
	% 	\lUC=\mathbb{E}\left[
	% 	\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
	% \end{equation}
	%
	%
	%Unabbreviated: Not Jinguan's version; 
	\begin{multline}
		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
		\eqand \bar{\unprojection}^i_{c,u,v}   =   
			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
		\eqand \\
		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
		\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
		{3\cdot128\cdot128\cdot L}
	\end{multline}
	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
	%  $(u,v,l)=s^n_{1...3,x,y}$
	$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
	for all 
	$n \in \{1...N\}$ , 
	$i \in \{1...L\}$ , 
	$x \in \{1...W\}$ , 
	$y \in \{1...H\}$ , 
	$U \in \{1...128\}$ , 
	$V \in \{1...128\}$.

@@

\subsection{Training Procedures}

	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
		TRITON w/o $\lUC$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
		TRITON w/o $\psi, \lUC$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).

	\subsubsection{TRITON}
	\label{par:triton}
	We train TRITON for 200,000 iterations on all datasets. This takes about 36-48 hours on an NVIDIA RTX A5000. 
	The dimension of each input scene is defined by hyperparameter height $H$; the width is scaled to match the aspect ratio of the original input.
	To avoid running out of video memory, we randomly crop each input to a $256\times256$ subset and run TRITON on that cropped input.
	We use batch size 5 during training.

	We found that the best way to train TRITON is to start with smaller $H$ values and progressively increase that value during training.
	For the first 50,000 iterations we use $H=320$, then for the next 50,000 iterations $H=420$, then for the last 100,000 iterations $H=\text{(the height of the original input scene)}$.

	\subsubsection{TRITON w/o $\lUC$}
	\label{par:triton_without_luc}
	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC$, discussed in \ref{par:munit_triton})
	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.

	\subsubsection{TRITON w/o $\psi, \lUC$}
	\label{par:munit_triton}
	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.

	\subsubsection{CycleGAN}
	\label{par:cyclegan}
	We use the original implementation of CycleGAN, and stick to the reccomended 200 epochs, as it tends to overfit if you go further. 
	For our tests, we run CycleGAN on multiple different scales of the input scenes, with input sizes $286\times286$ (CycleGAN's default), $320\times320$, $420\times420$ and $512\times512$. 
	After translation, we stretch the image into the input's aspect ratio.
	We also set $\lambda_{identity}=0$, meaning we disable the identity loss.
	The reported results are the calculated using the best results among these resolutions.
	This dramatically improves CycleGAN's performance when translating UVL scenes to photographs, as this loss was built with the assumption that some parts of the input should not be changed during translation (which is not true in our case).

	\subsubsection{CUT}
	\label{par:cut}
	We use the original implementation of CUT, and stick to the reccomended 400 epochs, as it tends to overfit if you go further. 
	Like with CycleGAN in \ref{par:cyclegan}, we run CUT on multiple different resolutions of the input scenes, with input sizes $286\times286$ (CUT's default), $320\times320$, $420\times420$ and $512\times512$. 
	After translation, we stretch the image into the input's aspect ratio.
	The reported results are the calculated using the best results among these resolutions.
